Parsing Tweets into Universal Dependencies

### 2017-11-09 paper.tex
update result, add motivation for ensemble, add abstract

\begin{document}
\maketitle
\begin{abstract}

\end{abstract}

@@

Universal dependencies \citep[UD]{NIVRE16.348} was created to deliver
consistent annotation across different languages. To allow such
consistency, UD was designed to be adaptive to different genres and languages
\cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. It's promising that analyzing
the syntax of tweets can benefit from such adaptability. In this paper,
we create a new tweets treebank of 55,607 tokens by following the UD
guidelines but also contending the domain-specific challenges which wasn't
covered by UD guidelines. Our annotation includes a whole pipeline of
tokenization, part-of-speech (POS) tags and universal dependencies.

@@

To achieve better performance without sacrificing efficiency, we propose
a new method to train the parser with the distillation 
\cite{DBLP:journals/corr/HintonVD15} of 20 parsers ensemble.
We show that learning from the exploration of the ensemble parser
can be more beneficial than just learning from the gold standard
transition sequence in the sense of training a transition-based
distilling parser. Experimental results show an improvement of more
than 3 points in LAS over baseline parser can be achieved with our
distillation method.

@@

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& \textcolor{green}{\bf @coldplay} \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl} \& Nice \& \textcolor{cyan}{\bf p} \& ...\\
			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny X \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \& \tiny ADJ \& \tiny X \& \tiny PUNCT \\
		\end{deptext}
		\deproot{1}{root}
		\depedge[edge unit distance=1em]{1}{2}{discourse}
		\deproot{6}{root}
		\depedge[edge unit distance=1em]{6}{3}{discourse}
		\depedge[edge unit distance=1em]{3}{4}{discourse}
		\depedge[edge unit distance=1em]{3}{5}{punct}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.8em]{6}{10}{obl}
		\depedge[edge unit distance=1em]{10}{8}{case}
		\depedge[edge unit distance=1em]{10}{9}{det}
		\depedge[edge unit distance=0.8em]{6}{11}{discourse}
		\depedge[edge unit distance=0.8em]{6}{12}{list}
		\deproot{13}{root}		
		\depedge[edge unit distance=0.8em]{13}{14}{discourse}
		\depedge[edge unit distance=0.8em]{13}{15}{punct}
	\end{dependency}
	\caption{An example tweet that contains non-syntactic tokens:
		\textcolor{red}{sentiment emoticon},
		\textcolor{orange}{retweet marker},
		\textcolor{green}{retweet at-mention},
		\textcolor{gray}{topical hashtag},
		\textcolor{blue}{referential URL}, and
		\textcolor{cyan}{truncated word}.}\label{fig:non-syn-toks}
\end{figure*}

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			@username \& its \& \#awesome \& u \& gonna \& $\heart$ \& it \& Chk \& out \& our \& cooool \& project \& on \& http:// \& + \& RT \& pls\\
			\tiny PROPN \& \tiny PRON \& \tiny ADJ \& \tiny PRON \& \tiny VERB \& \tiny VERB \& \tiny PRON \& \tiny VERB \& \tiny ADP \& \tiny PRON \& \tiny ADJ \& \tiny NOUN \& \tiny ADP \& \tiny X \& \tiny SYM \& \tiny VERB\& \tiny INTJ\\
		\end{deptext}
		\deproot{3}{root}
		\depedge[edge unit distance=1em]{3}{1}{vocative}
		\depedge[edge unit distance=1em]{3}{2}{nsubj}
		\depedge[edge unit distance=1em]{3}{5}{parataxis}
		\depedge[edge unit distance=1em]{5}{4}{nsubj}
		\depedge[edge unit distance=1em]{5}{6}{xcomp}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.7em]{3}{8}{parataxis}
		\depedge[edge unit distance=1em]{8}{9}{compound:prt}
		\depedge[edge unit distance=0.7em]{8}{12}{obj}
		\depedge[edge unit distance=1em]{12}{10}{nmod:poss}
		\depedge[edge unit distance=1em]{12}{11}{amod}
		\depedge[edge unit distance=0.6em]{8}{14}{obl}
		\depedge[edge unit distance=1em]{14}{13}{case}
		\depedge[edge unit distance=0.55em]{8}{16}{conj}
		\depedge[edge unit distance=1em]{16}{15}{cc}
		\depedge[edge unit distance=0.37em]{3}{17}{discourse}
	\end{dependency}
	\caption{An example tweet with informal but syntactic tokens.}\label{fig:informal-toks}
\end{figure*}

@@

\subsection{\sc Tweebank v2}
Following the guidelines mentioned above, we create a new annotated Twitter treebank, which we call {\sc Tweebank v2}.

@@

\subsubsection{Annotation Process}
Our annotation process was conducted in three stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1}
proportion and created the initial annotations in one day.
\nascomment{Check:} Before annotating, they were given a tutorial overview of the UD
annotation conventions and our guidelines.
Both the guidelines and annotation
were further refined by the authors of this paper to increase
the coverage of our guideline and solve inconsistency between
different annotators during this exercise. In the second stage, a POS tagger and
parser were trained on the annotated data from the first stage,
and used to automatically analyze the sampled 2,500 tweets.  Authors 
of this paper manually corrected the parsed data. \nascomment{this is
  a little weird:  don't you have to do this before you parse?} Finally, an extra
layer of word-level normalization was manually annotated.

\begin{figure}
\centering
\small
\begin{dependency}[edge slant=2, text only label, label style=above]
	\begin{deptext}
		Olympic \& gold \& medallist \& whipped \& by \& John \& Fisher \\
	\end{deptext}
	\deproot{3}{root}
	\depedge[edge unit distance=1em]{3}{1}{amod}
    \depedge[edge unit distance=1em]{3}{2}{compound}
    \depedge[edge unit distance=1em]{3}{4}{acl}
    \depedge[edge unit distance=1em]{4}{6}{obl}
    \depedge[edge unit distance=1em]{6}{5}{case}
    \depedge[edge unit distance=1em]{6}{7}{flat}
	\deproot[edge below]{4}{root}
%	\depedge[edge below, edge unit distance=1em]{3}{1}{amod}
%	\depedge[edge below, edge unit distance=1em]{3}{2}{compound}
	\depedge[edge below, edge unit distance=1em]{4}{3}{nsubj}
%	\depedge[edge below, edge unit distance=1em]{4}{6}{obl}
%	\depedge[edge below, edge unit distance=1em]{6}{5}{case}
%	\depedge[edge below, edge unit distance=1em]{6}{7}{flat}
\end{dependency}
\caption{An example of disagreement; one annotator's parse is shown above, disagreeing arcs from the other
  annotator are shown below.}\label{fig:disagree}
\end{figure}

@@

We introduce a new
character-level bidirectional LSTM (bi-LSTM) sequence-labeling model
\nascomment{add cite for this kind of model}
for tokenization.
Our model takes the raw sentence and tags each character in this 
sentence as whether it is the beginning of a word.
\nascomment{check:} It is trained on the training portion of
\textsc{Tweebank v2} combined with the UD\_English training dataset.

@@

We tested our tokenizer on the \textsc{Tweebank v2} test set. 
We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
tokenization results, compared to  other available tokenizers. 
\nascomment{Check:}  The Stanford \nascomment{cite}  and Twokenizer
\nascomment{cite} systems are rule-based systems and were not adapted
to the UD tokenization scheme.
The UD pipe v1.2
\cite{straka-strakova:2017:K17-3} model was re-trained on the same
data as our system.
Our bi-LSTM tokenizer achieves the best accuracy among all these
tokenizers.  These results indicate the value of statistical modeling
in tokenization for informal texts.

@@

Part-of-speech tagging for tweets has been extensively studied \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
On the annotation scheme designed in \S\ref{sec:pos-anno}, based on UD and adapted for
Twitter, we compared several existing systems and also two bi-LSTM systems similar
to \citet{??} \nascomment{add cite}, one using word vectors and the
other using word and character vectors.   All systems were re-trained on
the combination of the UD\_English and \textsc{Tweebank v2} training sets.

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & \it Precision \\
		\hline
%		Stanford Postagger & 65.6 \\
		Stanford CoreNLP & 90.4 \\
%		UD pipe v1.2 & 78.7 \\
		\citealp{owoputi-EtAl:2013:NAACL-HLT} (greedy) & 94.2 \\
		\citealp{owoputi-EtAl:2013:NAACL-HLT} (CRF) & \bf 95.1 \\
		\hdashline
%		UD pipe v1.2 & 83.8 \\
		\citealp{ma-hovy:2016:P16-1} & \\
		our word bi-LSTM & 89.1 \\
		our character + word bi-LSTMs & 91.4 \\
		\hline
	\end{tabular}
	\caption{POS tagger comparison on gold-standard tokens in the
          \textsc{Tweebank v2} test set. \label{tbl:pos-result}
          \nascomment{to do:  fill in Ma/Hovy}}
\end{table}

@@

We tested the POS taggers on \textsc{Tweebank v2} test set.  Results
with gold-standard tokenization are shown in
Table \ref{tbl:pos-result}. The careful feature engineering in the 
POS tagger  of \citet{owoputi-EtAl:2013:NAACL-HLT} outperforms our neural network
models.  (That tagger also makes use of \citet{Brown} clusters derived
from a large collection of unannotated tweets.  Those clusters did not
improve the performance of our bi-LSTM models.)

Results of the \citet{owoputi-EtAl:2013:NAACL-HLT}  with non-greedy
inference \nascomment{check} on automatically tokenized data
are shown in  Table \ref{tbl:pos-result-vs-tok}.  We see that errors
in tokenization do propagate, but tagging performance is above 93\%
with our tokenizer.

@@

%Time is a major concern on
Social media applications teypically require processing large volumes
of data, making speed an important criterion. We therefore 
use the neural greedy parser introduced by \newcite{ballesteros-EtAl:2016:EMNLP2016},
which can parse a sentence in linear time and harnesses 
character representations, which should help mitigate the challenge of
spelling variation. To further improve the parsing accuracy,
we propose a new method to distill an ensemble of 20 differently
initialized parsers into one parser.  To our knowledge, this is the
first attempt to distill an ensemble of greedy transition-based
parsers \nascomment{check}.

@@

\paragraph{Preliminary results.}
In our preliminary experiments, we train our parser on the combination of UD\_English
and \textsc{Tweebank v2} training sets. \nascomment{are we using
  gold-standard tokenization or automatic, here?} Automatic POS tags are assigned with 5-fold
jackknifing. Hyperparameters, including the value of $\alpha$ in Equation \ref{eq:distill},
are tuned on the \textsc{Tweebank v2} development set. 20 parsers are trained with
different random seeds and ensembled by averaging their output probability
distributions over transitions. The ensemble parser achieves a LAS of 78.8, which is more 
than 3 points higher than the baseline single parser. Distilling from this
parser leads to a single parser with  77.0 LAS.
%We first study the necessity of log-likelihood loss (the first term in Equation \ref{eq:distill}).

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{graphics/alpha}
	\caption{The effect of $\alpha$ on
          distillation. \nascomment{to do:  please make the font in
            the graphic readable}}\label{fig:effect-alpha}
\end{figure}

We further study the effect of the interpolation hyperparameter $\alpha$ by varying it from 0 to 1.
The results are shown in Figure \ref{fig:effect-alpha}. We can see that distilling parsers with larger $\alpha$ achieves better
performance, which means the model should pay more attention to learning
from the teacher model.  Indeed, the negligible difference between the
best performance at $\alpha = 0.9$ and $\alpha=1.0$ casts doubt on the
necessity of including $\mathcal{L}_{NNL}$ in the training objective
at all. \nascomment{check my rewording}

\paragraph{Learning from exploration.} We further set $\alpha$ to 1.0,
eliminating the oracle from the usual transition-based parser
training algorithm.  Instead of generating
training instances from the oracle, we generate them by random sampling
transitions from the teacher (ensemble \nascomment{check}) model's output distribution and follow the
trajectory of these transitions. We name this method \textsc{distill explore}.

\paragraph{Final results.}
\begin{table}[t]
	\centering
	\begin{tabular}{rcc}
		\hline
		\it System & UAS & LAS \\
		\hline
		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.2 & 75.4 \\
%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		Ensemble (20) & 83.0 & 78.8 \\
		\textsc{distill expert} ($\alpha$=1.0) & 81.2 & 76.7 \\
		\textsc{distill expert} ($\alpha$=0.9) & 81.4 & 77.0 \\		
		\textsc{distill explore} & 82.2 & 77.9 \\
		\hline
	\end{tabular}
	\caption{Dependency parser comparison on \textsc{Tweebank v2},
           with automatic POS tags. \label{tbl:parse-result}}
\end{table}

>>>>

\begin{document}
\maketitle
\begin{abstract}
In this paper, we study the problem of analyzing tweets with
universal dependencies \citep[UD]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets. Under such guidelines, we create
a new tweet treebank which has 55,607 tokens and it's more than 4 times
larger than the {\sc Tweebank v1}. We characterize the disagreements
among our annotation and show that it is challenging to deliver
consistent annotation due to the ambiguities in ways of
understanding and explaining the tweets. Over the new treebank,
we build a pipeline system to parse tweets into UD. To conquer the
annotation noise without sacrificing efficiency, we propose a new
method to distill an ensemble of 20 parsers into a single one. Our
method achieve an improvement of 2.3 in LAS over the baseline.
\end{abstract}

@@

Universal dependencies \citep[UD]{NIVRE16.348} was created to deliver
consistent annotation across different languages. To allow such
consistency, UD was designed to be adaptive to different genres and languages
\cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. It's promising that analyzing
the syntax of tweets can benefit from such adaptability. In this paper,
we create a new tweets treebank of 55,607 tokens by following the UD
guidelines but also contending the domain-specific challenges which wasn't
covered by UD guidelines. Our annotation includes a whole pipeline of
tokenization, part-of-speech (POS) tags and universal dependencies.
We characterize the disagreement among our annotations and show that
consistent annotation is still challenging to deliver even with
the extended guidelines.

@@

To conquer the noise in our annotation and achieve better performance
without sacrificing efficiency, we propose a new method to
train the parser with the distillation 
\cite{DBLP:journals/corr/HintonVD15} of 20 parsers ensemble.
We show that learning from the exploration of the ensemble parser
can be more beneficial than just learning from the gold standard
transition sequence in the sense of training a transition-based
distilling parser. Experimental results show an improvement of more
than 3 points in LAS over baseline parser can be achieved with our
distillation method.

@@

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& \textcolor{green}{\bf @coldplay} \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl} \& Nice \& \textcolor{cyan}{\bf p} \& ...\\
			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny X \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \& \tiny ADJ \& \tiny X \& \tiny PUNCT \\
		\end{deptext}
		\deproot{1}{root}
		\depedge[edge unit distance=1em]{1}{2}{discourse}
		\deproot{6}{root}
		\depedge[edge unit distance=1em]{6}{3}{discourse}
		\depedge[edge unit distance=1em]{3}{4}{discourse}
		\depedge[edge unit distance=1em]{3}{5}{punct}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.8em]{6}{10}{obl}
		\depedge[edge unit distance=1em]{10}{8}{case}
		\depedge[edge unit distance=1em]{10}{9}{det}
		\depedge[edge unit distance=0.8em]{6}{11}{discourse}
		\depedge[edge unit distance=0.8em]{6}{12}{list}
		\deproot{13}{root}		
		\depedge[edge unit distance=0.8em]{13}{14}{discourse}
		\depedge[edge unit distance=0.8em]{13}{15}{punct}
	\end{dependency}
	\caption{An example tweet that contains non-syntactic tokens:
		\textcolor{red}{sentiment emoticon},
		\textcolor{orange}{retweet marker},
		\textcolor{green}{retweet at-mention},
		\textcolor{gray}{topical hashtag},
		\textcolor{blue}{referential URL}, and
		\textcolor{cyan}{truncated word}.
		This example tweet is a concatenation of three real tweets.
	}\label{fig:non-syn-toks}
\end{figure*}

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			@username \& its \& \#awesome \& u \& gonna \& $\heart$ \& it \& Chk \& out \& our \& cooool \& project \& on \& http:// \& + \& RT \& pls\\
			\tiny PROPN \& \tiny PRON \& \tiny ADJ \& \tiny PRON \& \tiny VERB \& \tiny VERB \& \tiny PRON \& \tiny VERB \& \tiny ADP \& \tiny PRON \& \tiny ADJ \& \tiny NOUN \& \tiny ADP \& \tiny X \& \tiny SYM \& \tiny VERB\& \tiny INTJ\\
		\end{deptext}
		\deproot{3}{root}
		\depedge[edge unit distance=1em]{3}{1}{vocative}
		\depedge[edge unit distance=1em]{3}{2}{nsubj}
		\depedge[edge unit distance=1em]{3}{5}{parataxis}
		\depedge[edge unit distance=1em]{5}{4}{nsubj}
		\depedge[edge unit distance=1em]{5}{6}{xcomp}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.7em]{3}{8}{parataxis}
		\depedge[edge unit distance=1em]{8}{9}{compound:prt}
		\depedge[edge unit distance=0.7em]{8}{12}{obj}
		\depedge[edge unit distance=1em]{12}{10}{nmod:poss}
		\depedge[edge unit distance=1em]{12}{11}{amod}
		\depedge[edge unit distance=0.6em]{8}{14}{obl}
		\depedge[edge unit distance=1em]{14}{13}{case}
		\depedge[edge unit distance=0.55em]{8}{16}{conj}
		\depedge[edge unit distance=1em]{16}{15}{cc}
		\depedge[edge unit distance=0.37em]{3}{17}{discourse}
	\end{dependency}
	\caption{An example tweet with informal but syntactic tokens.
	This is an artificial tweets inspired by several tweets.}\label{fig:informal-toks}
\end{figure*}

@@

\subsection{\sc Tweebank v2}\label{sec:anno-process}
Following the guidelines mentioned above, we create a new annotated Twitter treebank, which we call {\sc Tweebank v2}.

@@

\subsubsection{Annotation Process}
Our annotation process was conducted in three stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1}
proportion and created the initial annotations in one day.
Before annotating, they were given a tutorial overview of the UD
annotation conventions and our guidelines.
Both the guidelines and annotation
were further refined by the authors of this paper to increase
the coverage of our guideline and solve inconsistency between
different annotators during this exercise. In the second stage, a POS tagger and
parser were trained on the annotated data from the first stage (1,041 tweets in total),
and used to automatically analyze the sampled 2,500 tweets.  Authors 
of this paper manually corrected the parsed data. \nascomment{this is
  a little weird:  don't you have to do this before you parse?} Finally, an extra
layer of word-level normalization was manually annotated for data
analysis purposes.

\begin{figure}
\centering
\small
\begin{dependency}[edge slant=2, text only label, label style=above]
	\begin{deptext}
		Olympic \& gold \& medallist \& whipped \& by \& John \& Fisher \\
	\end{deptext}
	\deproot{3}{root}
	\depedge[edge unit distance=1em]{3}{1}{amod}
    \depedge[edge unit distance=1em]{3}{2}{compound}
    \depedge[edge unit distance=1em]{3}{4}{acl}
    \depedge[edge unit distance=1em]{4}{6}{obl}
    \depedge[edge unit distance=1em]{6}{5}{case}
    \depedge[edge unit distance=1em]{6}{7}{flat}
	\deproot[edge below]{4}{root}
%	\depedge[edge below, edge unit distance=1em]{3}{1}{amod}
%	\depedge[edge below, edge unit distance=1em]{3}{2}{compound}
	\depedge[edge below, edge unit distance=1em]{4}{3}{nsubj}
%	\depedge[edge below, edge unit distance=1em]{4}{6}{obl}
%	\depedge[edge below, edge unit distance=1em]{6}{5}{case}
%	\depedge[edge below, edge unit distance=1em]{6}{7}{flat}
\end{dependency}
\caption{An example of disagreement; one annotator's parse is shown above, disagreeing arcs from the other
  annotator are shown below. This is a real example in our annotation.}\label{fig:disagree}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth,trim={0 0 13cm 9cm},clip]{graphics/bilstm_tokenizer}
	\caption{The bi-LSTM tokenizer model that segments `its gonna be' into `it s gon na be'.}\label{fig:tok-model}
\end{figure}
We introduce a new
character-level bidirectional LSTM (bi-LSTM) sequence-labeling model
\cite{DBLP:journals/corr/HuangXY15,ma-hovy:2016:P16-1}
for tokenization.
Our model takes the raw sentence and tags each character in this 
sentence as whether it is the beginning of a word (1 as the beginning and 0 otherwise).
Figure \ref{fig:tok-model} shows our tokenization model.
Space is treated as an input but consistently assigned a special tag \$.

@@

We trained our tokenizer on the training portion of
\textsc{Tweebank v2} combined with the UD\_English training dataset
and tested on the \textsc{Tweebank v2} test set. 
We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
tokenization results, compared to  other available tokenizers. 
The Stanford \cite{manning-EtAl:2014:P14-5} and Twokenizer
\cite{ICWSM101540} systems are rule-based systems and were not adapted
to the UD tokenization scheme.
The UD pipe v1.2
\cite{straka-strakova:2017:K17-3} model was re-trained on the same
data as our system.
Our bi-LSTM tokenizer achieves the best accuracy among all these
tokenizers.  These results indicate the value of statistical modeling
in tokenization for informal texts.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth,trim={0 0 13cm 3cm},clip]{graphics/bilstm_postagger}
	\caption{The bi-LSTM postagger model that tags `it s gon na be' as {\tt PRON AUX VERB PART AUX}.}\label{fig:pos-model}
\end{figure}

Part-of-speech tagging for tweets has been extensively studied \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
On the annotation scheme designed in \S\ref{sec:pos-anno}, based on UD and adapted for
Twitter, we compared several existing systems and also two bi-LSTM systems similar
to \citet{DBLP:journals/corr/HuangXY15} and \citet{lample-EtAl:2016:N16-1}, one using
word vectors and the other using word and character vectors (see Figure \ref{fig:pos-model}).
All systems were re-trained on the combination of the UD\_English and 
\textsc{Tweebank v2} training sets. We use the twitter specific glove embedding released by
\citet{pennington-socher-manning:2014:EMNLP2014} as the word embeeding in all the neural tagger
and parser\footnote{\url{http://nlp.stanford.edu/data/glove.twitter.27B.zip}}.

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & \it Precision \\
		\hline
%		Stanford Postagger & 65.6 \\
		Stanford CoreNLP & 90.4 \\
%		UD pipe v1.2 & 78.7 \\
		\citealp{owoputi-EtAl:2013:NAACL-HLT} (greedy) & 94.2 \\
		\citealp{owoputi-EtAl:2013:NAACL-HLT} (CRF) & \bf 95.1 \\
		\hdashline
%		UD pipe v1.2 & 83.8 \\
		\citealp{ma-hovy:2016:P16-1} & 91.8 \\
		our word bi-LSTM & 89.2 \\
		our character + word bi-LSTMs & 91.5 \\
		\hline
	\end{tabular}
	\caption{POS tagger comparison on gold-standard tokens in the
          \textsc{Tweebank v2} test set. \label{tbl:pos-result}}
\end{table}

@@

We tested the POS taggers on \textsc{Tweebank v2} test set.  Results
with gold-standard tokenization are shown in
Table \ref{tbl:pos-result}. The careful feature engineering in the 
POS tagger of \citet{owoputi-EtAl:2013:NAACL-HLT} outperforms our neural network
models.  (That tagger also makes use of \citet{Brown:1992:CNG:176313.176316} clusters derived
from a large collection of unannotated tweets.  Those clusters did not
improve the performance of our bi-LSTM models.)

Results of the \citet{owoputi-EtAl:2013:NAACL-HLT}  with non-greedy
inference on automatically tokenized data
are shown in  Table \ref{tbl:pos-result-vs-tok}.  We see that errors
in tokenization do propagate, but tagging performance is above 93\%
with our tokenizer.

@@

Social media applications typically require processing large volumes
of data, making speed an important criterion. We therefore 
use the neural greedy parser introduced by \newcite{ballesteros-EtAl:2016:EMNLP2016},
which can parse a sentence in linear time and harnesses 
character representations, which should help mitigate the challenge of
spelling variation. We encourage the reader to refer their paper for
more details about the model.

Section \ref{sec:anno-process} shows that severe ambiguities
exist when we create {\sc Tweebank v2}, which makes the training data
of the parser very noisy. \citet{Frnay2014ClassificationIT} suggested
that most of losses are shown to be not robust to 
classification noise, including the log-likelihood loss used in
\citet{ballesteros-dyer-smith:2015:EMNLP}. To conquer the noisy
data and further improve the parsing accuracy, we followed the
empirical study of \citet{Dietterich2000} and ensemble of 20 differently
initialized parsers. To make it still parses in linear time, we
propose a new method to distill the ensemble of 20 parsers into one parser.
To our knowledge, this is the first attempt to distill an
ensemble of greedy transition-based
parsers.% \nascomment{check}.

@@

\paragraph{Preliminary results.}
In our preliminary experiments, we train our parser on the combination of UD\_English
and \textsc{Tweebank v2} training sets. Gold-standard tokenization and automatic POS
tags are used. Automatic POS tags are assigned with 5-fold
jackknifing. Hyperparameters, including the value of $\alpha$ in Equation \ref{eq:distill},
are tuned on the \textsc{Tweebank v2} development set. Unlabeled attachment score and
labeled attachment score including punctuations are used to evaluate parsing performance.

\citet{reimers-gurevych:2017:EMNLP2017} pointed out that the training process for neural networks are highly
non-deterministic and largely depends on the seed value for pseduo-random number generator.
Our preliminary experiments confirm this finding by witnessing a gap of 1 LAS on development set
between the best (75.8) and worst (74.8) runs. To eliminate the effect of random number, for each
hyperparameter setting, we conduct 5 runs with different seeds and report the averaged score.

Our 20 parsers are ensembled by averaging their output probability
distributions over transitions. The ensemble parser achieves a LAS of 79.4, which is more 
than 3 points higher than the baseline single parser. Distilling from this
parser leads to a single parser with 78.1 LAS.
%We first study the necessity of log-likelihood loss (the first term in Equation \ref{eq:distill}).

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth,trim={0.3cm 0 0 0},clip]{graphics/alpha}
	\caption{The effect of $\alpha$ on \textsc{expert distillation}.}\label{fig:effect-alpha}
\end{figure}

We further study the effect of the interpolation hyperparameter $\alpha$ by varying it from 0 to 1.
The results are shown in Figure \ref{fig:effect-alpha}. We can see that distilling parsers with larger $\alpha$ achieves better
performance, which means the model should pay more attention to learning
from the teacher model.  Indeed, the negligible difference between the
best performance at $\alpha = 0.9$ and $\alpha=1.0$ casts doubt on the
necessity of including $\mathcal{L}_{NNL}$ in the training objective
at all.% \nascomment{check my rewording}

\paragraph{Learning from exploration.} We further set $\alpha$ to 1.0,
eliminating the oracle from the usual transition-based parser
training algorithm.  Instead of generating
training instances from the oracle, we generate them by random sampling
transitions from the teacher (ensemble) model's output distribution and follow the
trajectory of these transitions. We name this method \textsc{distill explore}.

\paragraph{Final results.}
\begin{table}[t]
	\centering
	\begin{tabular}{rcc}
		\hline
		\it System & UAS & LAS \\
		\hline
		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.4 & 75.8 \\
%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		Ensemble (20) & 83.5 & 79.4 \\
		\textsc{distill expert} ($\alpha$=1.0) & 82.2 & 78.0 \\
		\textsc{distill expert} ($\alpha$=0.9) & 82.4 & 78.1 \\		
		\textsc{distill explore} & 82.5 & 78.4 \\
		\hline
	\end{tabular}
	\caption{Dependency parser comparison on \textsc{Tweebank v2},
           with automatic POS tags. \label{tbl:parse-result}}
\end{table}
